Discrete Quantum Theories and Computing

### 2018-12-04 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Add a table to summarize the results...

%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,twoside]{iuphd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage[all]{xy}

@@

@@

\begin{table}
\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical computational
models and their physical realizations\todo{Put the third row in
the middle alignment.}}
\begin{tabularx}{\linewidth}{ccX}
\toprule 
\addlinespace
 & Discrete & Continuum\tabularnewline\addlinespace
\midrule
\addlinespace
\midrule
\addlinespace
Theoretical  Model & Turing machine & BCSS machine\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Physical Realization & Digital Computer & Analog Computer\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
How the models realize? & Reliably & Not Reliably:
\begin{itemize}
\item The quality might be quantized.
\item The precision of an analog computer is low.
\end{itemize}\tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabularx}
\end{table}
The situations for classical computation is summarized in Table~\ref{tab:Comparison},
and similar situations could potentially be applied to quantum computation.
\todo{Introduction cleaning up until here. }Similar to classical
analog computers manipulating, say, the position of substance, the
most widely used model of quantum computing, the quantum circuit model,
manipulates the probability amplitudes to do the computation. \todo{Play
with some cloud quantum computers to see if I can find more support
evidence. }Because we are agnostic about whether probability amplitude
is quantized or can really be valued in the continuum of complex numbers,
we tried to develop two different types of models: the quantum theories
and computing over finite fields are discrete models, and the quantum
interval-valued probability measures incorporate the idea of measurement
precision into the quantum theory. To distinguish the modified quantum
theories from the usual ones, the usual ones will be called the ``conventional
quantum theory'' where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
and ``ordinary'' quantum theory.}.

\todo{Beginning of Merge Left}Since conventional probability amplitude
is in the field of complex numbers, and the field structure is essential
to compute the probability from some probability amplitudes, we in
Chapter~\ref{chap:DQT=000026DQC} tried to build discrete quantum
theories and computing by considering them over finite fields.

@@

\section{Discrete Quantum Theory (I): Geometry of Entangled States}

@@

\section{Discrete Quantum Theory (II)}

>>>>

%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,twoside]{iuphd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{verbatim}
\usepackage{rotfloat}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage[all]{xy}

@@

\todo{Maybe start with this kind of sentence “We want a more faithful
quantum theory not only because the current quantum theory don't take
into account of the measurement precision, but also because its computational
model doesn't fit the current development of computer science.”
}\todo{See if we can cite this paper~\cite{Gisin2017} for finite
precision measurement. }

\todo{新的大綱：主旨：probability amplitude到底是離散還是連續的？
\begin{itemize}
\item Some quantities are obvious discrete, but how to model other quantities
which we don't know?
\begin{itemize}
\item 一尺之槌，日取其半，萬世不竭。
\item Zeno 追龜的故事
\item $\sqrt{2}$是無理數謀殺案(物理量？)
\item Euclid?(物理量？)
\end{itemize}
當我們的儀器不足以分辨出最小單位時，假設沒有最小單位很合理，而且可以很好的解釋我們觀察到的現象。
\item 很多大家本來相信是連續的物理量最後被證明是離散的：
\begin{itemize}
\item “一尺之槌，日取其半，萬世不竭。”是錯的。
\item 光電效應
\item 角動量(角度？)
\end{itemize}
\end{itemize}
}

@@

\begin{table}
\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical computational
models and their physical realizations\todo{Put the third row in
the middle alignment.}}
\begin{tabularx}{\linewidth}{ccX}
\toprule 
\addlinespace
 & Discrete & Continuum\tabularnewline\addlinespace
\midrule
\addlinespace
\midrule
\addlinespace
Theoretical  Model & Turing machine & BCSS machine\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
Physical Realization & Digital Computer & Analog Computer\tabularnewline\addlinespace
\addlinespace
\midrule
\addlinespace
How the models realize? & Reliably & Not Reliably:
\begin{itemize}
\item The quality might be quantized.
\item The precision of an analog computer is low.
\end{itemize}\tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabularx}
\end{table}
The situations for classical computation is summarized in Table~\ref{tab:Comparison},
and similar situations could potentially be applied to quantum computation.
\todo{Introduction cleaning up until here. }Similar to classical
analog computers manipulating, say, the position of substance, the
most widely used model of quantum computing, the quantum circuit model,
manipulates the probability amplitudes to do the computation. \todo{Play
with some cloud quantum computers to see if I can find more support
evidence. }Because we are agnostic about whether probability amplitude
is quantized or can really be valued in the continuum of complex numbers,
we tried to develop two different types of models: the quantum theories
and computing over finite fields are discrete models, and the quantum
interval-valued probability measures incorporate the idea of measurement
precision into the quantum theory. To distinguish the modified quantum
theories from the usual ones, the usual ones will be called the ``conventional
quantum theory'' where necessary and it will be reviewed in Chapter~\ref{chap:Conventional-Quantum-Theory}~\footnote{Alternative terminology in the literature includes ``actual,'' ``standard,''
and ``ordinary'' quantum theory.}.
\begin{sidewaystable}
\caption{Comparison among our models}

\centering{}%
\begin{tabular}{ccccccc}
\toprule 
\addlinespace
 & Conventional & Modal & Discrete (I) & Discrete (II) & QPMFF & QIVPM\tabularnewline\addlinespace
\midrule
\addlinespace
\midrule 
\addlinespace
 & Chapter~\ref{chap:Conventional-Quantum-Theory} & Sec.~\ref{modalquantum} & Sec.~\ref{discretequantumtheoryI} to \ref{sec:Geometry-of-Entangled-States} & Sec.~\ref{sec:Discrete-Quantum-Theory-(II)} & Sec.~\ref{sec:Toward-IVPM} & Chapter~\ref{chap:QIVPM}\tabularnewline\addlinespace
\midrule
\addlinespace
\addlinespace
States Space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Local Region\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
in $\Fpp^{D}$\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & $\Fpp^{D}$ & $\mathbb{C}^{D}$\tabularnewline\addlinespace
\addlinespace
\addlinespace
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Prediction\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
of Events\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & %
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Real-Valued\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Probability\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & %
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Possible or\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Impossible\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & %
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Possible or\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Impossible\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & %
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Cardinal\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Probability\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & %
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Real-Valued\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Probability, but no\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
sensible Born rule\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & %
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Interval-Valued\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Probability\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular}\tabularnewline\addlinespace
\addlinespace
\addlinespace
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Expectation\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Values\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & Defined &  &  & Undefined &  & Defined\tabularnewline\addlinespace
\midrule
\addlinespace
\midrule 
\addlinespace
 &  & Sec.~\ref{modalquantumcomputing} & Sec.~\ref{discretequantumcomputingI} & Sec.~\ref{discretequantumcomputingII} &  & \tabularnewline\addlinespace
\midrule
\addlinespace
\addlinespace
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Hadamard\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Transformation\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & Included & %
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
May not be\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Included\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & Included & Included &  & \tabularnewline\addlinespace
\addlinespace
\addlinespace
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Solve\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
$\usat$\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Efficiently\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & Unlikely & Yes & Partially & No &  & \tabularnewline\addlinespace
\addlinespace
\addlinespace
\begin{tabular}{c}
\noalign{\vskip\doublerulesep}
Grover Search\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\noalign{\vskip\doublerulesep}
Algorithm\tabularnewline[\doublerulesep]
\noalign{\vskip\doublerulesep}
\end{tabular} & Yes &  &  & Yes &  & \tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabular}
\end{sidewaystable}
\todo{Beginning of Merge Left}Since conventional probability amplitude
is in the field of complex numbers, and the field structure is essential
to compute the probability from some probability amplitudes, we in
Chapter~\ref{chap:DQT=000026DQC} tried to build discrete quantum
theories and computing by considering them over finite fields.

@@

\section{Discrete Quantum Theory (I): Geometry of Entangled States\label{sec:Geometry-of-Entangled-States}}

@@

\section{Discrete Quantum Theory (II)\label{sec:Discrete-Quantum-Theory-(II)}}
